Dependent Object Types

### 2012-08-06 article.tex
minor rewording

By operational semantics, $\reductionl {t_1'.l_i} {s'} {t'} {s'}
1$. Since ${t_1'} \in \relv {k-j} {\Gamma'} {s'} {T_1}$, we can
conclude $t' \in \relv {k-j-1} {\Gamma'} {s'} T$ from the clause for
value labels.

@@

By operational semantics, $\reductionl {t_1'.m_i(v_2)} {s_{12}}
{\subst {v_2} {x_i} {t_i}} {s_{12}} 1$.

>>>>

By operational semantics and the above, $\reductionl {t_1'.l_i} {s'}
{t'} {s'} 1$, and we can conclude $t' \in \relv {k-j-1} {\Gamma'} {s'}
T$ from the clause for value labels of ${t_1'} \in \relv {k-j}
{\Gamma'} {s'} {T_1}$.

@@

By the above and operational semantics, $\reductionl {t_1'.m_i(v_2)}
{s_{12}} {\subst {v_2} {x_i} {t_i}} {s_{12}} 1$.
